Analysis for Project

### 2021-03-26 analysis/analysis.Rmd
added lpm models; function for generating difference plots; summary of variables by race

>>>>

```{r}
#try a LPM
model1_lpm <- lm(below_exp_grade~race+as.factor(year), data=acs)
model2_lpn <- update(model1, .~.+degree_mother+degree_father)
model3_lpm <- update(model2, .~.+sqrt(family_income/10000)+own_home+parents_married)
model4_lpm <- update(model3, .~.+foreign_born_mother+foreign_born_father)

knitreg(list(model1_lpm, model2_lpm, model3_lpm, model4_lpm), digits=3)
```

```{r}
plot_mr_effects <- function(model) {
  coef_table <- tidy(model) %>%
    filter(str_detect(term, "race") & str_detect(term, "/") & !str_detect(term, "Multiracial")) %>%
    mutate(term=str_remove(term, "race"))

  #add in the placements for each single race group
  single_race <- tidy(model) %>%
    filter(str_detect(term, "race") & !str_detect(term, "/") & !str_detect(term, "Multiracial")) %>%
    select(term, estimate) %>%
    mutate(term=str_remove(term, "race"))
  x <- c(0, single_race$estimate)
  names(x) <- c("White",single_race$term)
  coef_table$lower <- NA
  coef_table$higher <- NA
  for(i in 1:nrow(coef_table)) {
    groups <- str_split(coef_table$term[i], "/")[[1]]
    temp <- diff(sort(x[groups]))/2
    coef_table$lower[i] <- -temp
    coef_table$higher[i] <- temp
  }

  # ggplot(coef_table, aes(x=reorder(term, estimate, mean), y=estimate, 
  #                        ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error))+
  #   geom_hline(yintercept = 0, linetype=2)+
  #   geom_pointrange()+
  #   geom_point(aes(x=reorder(term, estimate, mean), y=higher, color="red"))+
  #   geom_point(aes(x=reorder(term, estimate, mean), y=lower, color="red"))+
  #   coord_flip()+
  #   theme_bw()

  ggplot(coef_table, aes(x=reorder(term, higher, mean), y=estimate, 
                         ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error))+
    geom_hline(yintercept = 0, linetype=2)+
    geom_pointrange()+
    geom_point(aes(x=reorder(term, higher, mean), y=higher, color="red"))+
    geom_point(aes(x=reorder(term, higher, mean), y=lower, color="red"))+
    coord_flip()+
    theme_bw()
}
```

```{r}
plot_mr_effects(model1)
```

```{r}
plot_mr_effects(model4)
```

```{r}
resources_race <- acs %>% 
  group_by(race) %>%
  summarize(mean_age=mean(age),
            prop_foreign_born=mean(foreign_born),
            mean_fam_inc=mean(family_income),
            prop_own_home=mean(own_home),
            prop_parents_married=mean(parents_married),
            mean_age_parents=mean((age_birth_mother+age_birth_father)/2),
            prop_parent_foreign_born=mean(foreign_born_father | foreign_born_mother)) %>%
  ungroup() %>%
  filter(!str_detect(race,"Multiracial"))

ggplot(resources_race, aes(x=reorder(race, mean_fam_inc, mean), y=mean_fam_inc))+
  geom_col()+
  coord_flip()
```
